Hypertension and microbiome

### 2019-04-25 articletwo.Rmd
Forest plot getting ready

>>>>

```{r salt}
lacto.meta <- meta(pseq.genus) %>%
    tibble::rownames_to_column("id")

lacto.abund <- subset_taxa(pseq.genus, Genus=="Lactobacillus") %>%
    abundances(., transform = "clr") %>%
    t %>%
    as.data.frame %>%
    tibble::rownames_to_column("id") %>%
    setNames(tolower(replace.brackets(names(.))))

lacto.full <- full_join(lacto.meta, lacto.abund, by = "id") %>%
    dplyr::mutate(fake_salt = relevel(factor(dplyr::ntile(BL_AGE, 4)), ref='1'),
                  lacto_groups = relevel(factor(dplyr::ntile(lactobacillus.bacteria, 4)), ref='1'))

lacto.mean <- lacto.full %>%
    group_by(fake_salt) %>%
    summarize(estimate = t.test(lactobacillus.bacteria)$"estimate",
              conf.low = t.test(lactobacillus.bacteria)$"conf.int"[1],
              conf.high = t.test(lactobacillus.bacteria)$"conf.int"[2]) %>%
    dplyr::rename(term = fake_salt)

lacto.odds <- glm(HYPERTENSION ~ lacto_groups, family = binomial(link=logit), data=lacto.full) %>%
    broom::tidy(conf.int = TRUE, conf.level = 0.95, exponentiate = TRUE) %>%
    filter(!grepl("Intercept", term)) %>%
    select(term, estimate, conf.low, conf.high) %>%
    add_row(term = "lacto_groups1", estimate = 1.0, conf.low = NA, conf.high = NA)

lacto.mean
lacto.odds
```

```{r forest plot lacto, eval = FALSE}

myforestplot <- function(data, xlab = "", ylab = "", ylimits = c(0,10), interceptone = FALSE) {
    ggplot(data = data,
           aes(x = term, y = estimate, ymin = conf.low, ymax = conf.high)) +
        geom_point() +
        { if (interceptone) geom_hline(aes(fill=fake_salt), yintercept=1, linetype=2) } +
        geom_errorbar(width=0.1,cex=1)+ 
        ggplot2::theme_minimal()  +
        theme(plot.title=element_text(size=16),
              axis.title=element_text(size=12),
              strip.background = element_blank()) +
        scale_y_continuous(limits = ylimits) +
        theme(panel.border = element_blank(),
              panel.grid.major = element_blank(),
              panel.grid.minor = element_blank(),
              axis.line = element_line(colour = "black")) +
        scale_x_discrete(labels=c("Q1", "Q2", "Q3", "Q4")) +
        xlab(xlab) +
        ylab(ylab)
}

gsalt <- grid.arrange(
    myforestplot(lacto.mean,
                 xlab = "Dieritary salt",
                 ylab = "Lactobacillus abundance",
                 ylimits = c(2,3)),
    myforestplot(lacto.odds,
                 xlab = "Lactobacillus abundance",
                 ylab = "Odds of hypertension",
                 ylimits = c(0.5, 1.5),
                 interceptone = TRUE),
    ncol=2)
ggsave(file = "cache/salt-forest.png", plot=gsalt, height=6, width=9)
